Neural Sparse Gaussian Process: For Updated Exploration

### 2023-04-14 paper/main.tex
Cleaning up
Change template to 2023

% NeurIPS packages
\usepackage[preprint]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

@@

\section{Introduction} \label{sec:intro}

@@

@@

\section{Method}
In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.

@@

\phantomsection%
\addcontentsline{toc}{section}{References}
\begingroup
\small
\bibliographystyle{abbrvnat}
\bibliography{main-blx,zotero-library,bibliography}
\endgroup

>>>>

% NeurIPS packages
\usepackage[]{neurips_2023}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors

@@

\section{Introduction}
\label{sec:intro}
%

@@

\begin{figure}[t!]
  \setlength{\figurewidth}{.48\textwidth}
  \setlength{\figureheight}{.5\figurewidth}
  \begin{subfigure}{.48\textwidth}
    \centering
    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \centering
    \tikz\node[fill=black!10,minimum width=\figurewidth,minimum height=\figureheight,rounded corners=5pt]{};
  \end{subfigure}
  \caption{Teaser figure goes here.}
  \label{fig:teaser}  
\end{figure}

@@

\section{Methods}
In the next section we show how we can obtain a SVGP directly from 1) a trained NN and 2) a BNN posterior.

@@

\phantomsection%
\addcontentsline{toc}{section}{References}
\begingroup
\small
\bibliographystyle{abbrvnat}
\bibliography{zotero-library,bibliography}
\endgroup
